### 2014-01-24 rscripts/manuscript.Rnw
add discussion of covert comms model

>>>>

The simulation runner sends \texttt{Time(t:Long)} messages to all actors in the simulation to indicate the march of time.  In general, during each time step a leader may initiate a new \texttt{Bad} message.  Other members of the covert group circulate \texttt{Bad} messages subsequent to receiving a \texttt{Bad} message themselves, with different probabilities for sending messages to superiors, collaborators, and subordinates.  Those probabilities do not depend on the origin of the received message (though this could be a useful mechanical tweak to the model).

Though those probabilities could be coded into the actors
